My thesis

### 2020-02-04 manuscript/index/index.Rmd

---
author: 'Gerbrich Ferdinands'
date: 'May 2020'
institution: 'Utrecht University'
division: 'Faculty of Social Sciences'
advisor: 'prof. dr. Rens van de Schoot'
# If you have more two advisors, un-silence line 7
altadvisor: 'Jonathan de Bruin, Raoul Schram'
department: 'Methodology and Statistics'
degree: 'Master of Science'
title: 'My thesis'
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
  thesisdown::thesis_pdf: default # yet fails to compile 
  thesisdown::thesis_gitbook: default # creates html book in _book folder.  
#  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default
# If you are creating a PDF you'll need to write your preliminary content (e.g., abstract, acknowledgements) here or
# use code similar to line 22-23 for the .RMD files. If you are NOT producing a PDF, you can delete or silence lines 21-32 in this YAML header.
abstract: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = '\n  ')`
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab is 
# needed on the line after the `|`.
#acknowledgements: |
#  I want to thank a few people.
#dedication: |
#  You can have a dedication here if you wish. 
#preface: |
#  This is an example of a thesis setup to use the reed thesis document class
#  (for LaTeX) and the R bookdown package, in general.
# Specify the location of the bibliography below
bibliography: bib/asreview.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
lot: true
lof: true
# If you prefer blank lines between paragraphs, un-silence lines  40-41 (this requires package tikz)
#header-includes:
#- \usepackage{tikz}
---

@@

# Introduction {.unnumbered}

- Importance of sound systematic reviews (meta)
- Why it was built
- Advantages over other types

- Whereas first results look promising, there hasn’t been conducted a full proof of concept

Goals: 
- Save time 
- But also more systematic..?

? Misses

>>>>

---
author: 'Gerbrich Ferdinands'
date: 'May 2020'
institution: 'Utrecht University'
division: 'Faculty of Social Sciences'
advisor: 'prof. dr. Rens van de Schoot'
# If you have more two advisors, un-silence line 7
altadvisor: 'Jonathan de Bruin, Raoul Schram'
department: 'Methodology and Statistics'
degree: 'Master of Science'
title: 'My thesis'
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
#  thesisdown::thesis_pdf: default  
  thesisdown::thesis_gitbook: default # creates html book in _book folder.  
#  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default
# If you are creating a PDF you'll need to write your preliminary content (e.g., abstract, acknowledgements) here or
# use code similar to line 22-23 for the .RMD files. If you are NOT producing a PDF, you can delete or silence lines 21-32 in this YAML header.
abstract: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = '\n  ')`
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab is 
# needed on the line after the `|`.
#acknowledgements: |
#  I want to thank a few people.
#dedication: |
#  You can have a dedication here if you wish. 
#preface: |
#  This is an example of a thesis setup to use the reed thesis document class
#  (for LaTeX) and the R bookdown package, in general.
# Specify the location of the bibliography below
bibliography: bib/asreview.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
lot: true
lof: true
# If you prefer blank lines between paragraphs, un-silence lines  40-41 (this requires package tikz)
#header-includes:
#- \usepackage{tikz}
---

@@

# Introduction {.unnumbered}
ASReview takes the following parameters/arguments:

- a model
- a query strategy
- a balance strategy (fixed)
- a feature extraction strategy
- number of training data

The model is typically a learning algorithm used to predict the relevance of text. The following models will be compared:

* Naive Bayes (*nb*) [@Zhang2004]. 
*
